### 2020-09-20 serial_analysis.tex
forgot to commit

% Created by tikzDevice version 0.12.3 on 2020-05-27 22:31:58
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (867.24,289.08);
\begin{scope}
\path[clip] ( 10.17,  0.00) rectangle (278.91,289.08);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 10.17,  0.00) rectangle (278.91,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 44.82, 30.69) rectangle (273.41,266.42);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (210.00,195.87) {maximum observable};

\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 95.70, 74.43) {minimum observable};

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (130.54,266.42) --
	(137.68,259.28) --
	(144.83,252.14) --
	(151.97,244.99) --
	(159.11,237.85) --
	(166.26,230.71) --
	(173.40,223.56) --
	(180.54,216.42) --
	(187.69,209.27) --
	(194.83,202.13) --
	(201.97,194.99) --
	(209.12,187.84) --
	(216.26,180.70) --
	(223.40,173.56) --
	(230.55,166.41) --
	(237.69,159.27) --
	(244.83,152.13) --
	(251.98,144.98) --
	(259.12,137.84) --
	(266.27,130.70) --
	(273.41,123.55);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 44.82,116.41) --
	( 51.96,109.26) --
	( 59.10,102.12) --
	( 66.25, 94.98) --
	( 73.39, 87.83) --
	( 80.53, 80.69) --
	( 87.68, 73.55) --
	( 94.82, 66.40) --
	(101.96, 59.26) --
	(109.11, 52.12) --
	(116.25, 44.97) --
	(123.39, 37.83) --
	(130.54, 30.69);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 44.82,137.84) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 59.10,219.10) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.25,183.08) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.39,194.99) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 80.53,194.99) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.68,223.56) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.82,223.56) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.96,194.99) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.11,216.42) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.25,184.27) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.39,159.58) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.54,159.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.68,165.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.83,150.04) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.97,160.95) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.11,149.30) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.26,144.74) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.40,149.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.54,133.26) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.69,138.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.83,129.96) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.97,127.28) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.12,127.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (216.26,119.77) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (223.40,115.57) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (230.55,124.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (237.69,122.12) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (244.83,109.26) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (259.12, 87.83) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (273.41, 73.55) circle (  1.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.82,137.84) --
	( 44.82,137.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.82,137.84) --
	( 44.82,137.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.82,137.84) --
	( 44.82,137.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.10,236.60) --
	( 59.10,236.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.10,236.60) --
	( 59.10,191.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.10,191.59) --
	( 59.10,191.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.25,227.49) --
	( 66.25,227.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.25,227.49) --
	( 66.25,152.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.25,152.84) --
	( 66.25,152.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.39,208.56) --
	( 73.39,208.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.39,208.56) --
	( 73.39,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.39,181.41) --
	( 73.39,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,236.42) --
	( 80.53,236.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,236.42) --
	( 80.53,141.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,141.41) --
	( 80.53,141.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.68,223.56) --
	( 87.68,223.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.68,223.56) --
	( 87.68,223.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.68,223.56) --
	( 87.68,223.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.82,257.49) --
	( 94.82,257.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.82,257.49) --
	( 94.82,189.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.82,189.63) --
	( 94.82,189.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.96,208.56) --
	(101.96,208.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.96,208.56) --
	(101.96,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.96,181.41) --
	(101.96,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.11,216.42) --
	(109.11,216.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.11,216.42) --
	(109.11,216.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.11,216.42) --
	(109.11,216.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.25,214.81) --
	(116.25,214.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.25,214.81) --
	(116.25,159.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.25,159.81) --
	(116.25,159.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.39,229.99) --
	(123.39,229.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.39,229.99) --
	(123.39,109.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.39,109.98) --
	(123.39,109.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.54,212.85) --
	(130.54,212.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.54,212.85) --
	(130.54,126.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.54,126.23) --
	(130.54,126.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.68,198.92) --
	(137.68,198.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.68,198.92) --
	(137.68,122.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.68,122.84) --
	(137.68,122.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (144.83,212.31) --
	(144.83,212.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (144.83,212.31) --
	(144.83,109.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (144.83,109.26) --
	(144.83,109.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.97,223.56) --
	(151.97,223.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.97,223.56) --
	(151.97,122.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.97,122.30) --
	(151.97,122.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,222.31) --
	(159.11,222.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,222.31) --
	(159.11, 91.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11, 91.58) --
	(159.11, 91.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.26,191.77) --
	(166.26,191.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.26,191.77) --
	(166.26,109.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.26,109.26) --
	(166.26,109.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (173.40,190.52) --
	(173.40,190.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (173.40,190.52) --
	(173.40,116.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (173.40,116.41) --
	(173.40,116.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (180.54,167.13) --
	(180.54,167.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (180.54,167.13) --
	(180.54, 87.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (180.54, 87.48) --
	(180.54, 87.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (187.69,193.74) --
	(187.69,193.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (187.69,193.74) --
	(187.69, 80.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (187.69, 80.69) --
	(187.69, 80.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (194.83,181.77) --
	(194.83,181.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (194.83,181.77) --
	(194.83, 87.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (194.83, 87.48) --
	(194.83, 87.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (201.97,172.84) --
	(201.97,172.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (201.97,172.84) --
	(201.97, 44.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (201.97, 44.97) --
	(201.97, 44.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.12,167.84) --
	(209.12,167.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.12,167.84) --
	(209.12, 70.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.12, 70.69) --
	(209.12, 70.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.26,144.98) --
	(216.26,144.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.26,144.98) --
	(216.26, 79.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.26, 79.26) --
	(216.26, 79.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.40,142.13) --
	(223.40,142.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.40,142.13) --
	(223.40, 92.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.40, 92.12) --
	(223.40, 92.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.55,144.98) --
	(230.55,144.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.55,144.98) --
	(230.55, 98.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.55, 98.55) --
	(230.55, 98.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,130.70) --
	(237.69,130.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,130.70) --
	(237.69,109.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,109.98) --
	(237.69,109.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.83,109.26) --
	(244.83,109.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.83,109.26) --
	(244.83,109.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.83,109.26) --
	(244.83,109.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (259.12, 87.83) --
	(259.12, 87.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (259.12, 87.83) --
	(259.12, 87.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (259.12, 87.83) --
	(259.12, 87.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (273.41,107.48) --
	(273.41,107.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (273.41,107.48) --
	(273.41, 39.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (273.41, 39.62) --
	(273.41, 39.62);

>>>>

% Created by tikzDevice version 0.12.3 on 2020-09-20 18:46:20
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,578.16);
\begin{scope}
\path[clip] (  0.00,289.08) rectangle (289.08,578.16);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,289.08) rectangle (289.08,578.16);
\end{scope}
\begin{scope}
\path[clip] ( 31.71,319.77) rectangle (283.58,555.50);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.71,319.77) rectangle (283.58,555.50);
\definecolor{fillColor}{gray}{0.35}

\path[fill=fillColor] ( 31.71,319.77) rectangle ( 38.40,323.18);

\path[fill=fillColor] ( 46.57,319.77) rectangle ( 53.26,326.60);

\path[fill=fillColor] ( 54.00,319.77) rectangle ( 60.69,330.02);

\path[fill=fillColor] ( 61.43,319.77) rectangle ( 68.12,326.60);

\path[fill=fillColor] ( 68.86,319.77) rectangle ( 75.55,330.02);

\path[fill=fillColor] ( 76.29,319.77) rectangle ( 82.98,323.18);

\path[fill=fillColor] ( 83.72,319.77) rectangle ( 90.41,326.60);

\path[fill=fillColor] ( 91.15,319.77) rectangle ( 97.84,330.02);

\path[fill=fillColor] ( 98.58,319.77) rectangle (105.27,326.60);

\path[fill=fillColor] (106.01,319.77) rectangle (112.70,333.43);

\path[fill=fillColor] (113.44,319.77) rectangle (120.13,374.43);

\path[fill=fillColor] (120.87,319.77) rectangle (127.56,374.43);

\path[fill=fillColor] (128.30,319.77) rectangle (134.99,381.26);

\path[fill=fillColor] (135.73,319.77) rectangle (142.42,384.68);

\path[fill=fillColor] (143.16,319.77) rectangle (149.84,439.34);

\path[fill=fillColor] (150.59,319.77) rectangle (157.27,483.76);

\path[fill=fillColor] (158.02,319.77) rectangle (164.70,494.01);

\path[fill=fillColor] (165.45,319.77) rectangle (172.13,487.17);

\path[fill=fillColor] (172.88,319.77) rectangle (179.56,507.67);

\path[fill=fillColor] (180.31,319.77) rectangle (186.99,535.00);

\path[fill=fillColor] (187.74,319.77) rectangle (194.42,545.25);

\path[fill=fillColor] (195.17,319.77) rectangle (201.85,487.17);

\path[fill=fillColor] (202.60,319.77) rectangle (209.28,476.92);

\path[fill=fillColor] (210.03,319.77) rectangle (216.71,480.34);

\path[fill=fillColor] (217.46,319.77) rectangle (224.14,466.67);

\path[fill=fillColor] (224.89,319.77) rectangle (231.57,425.68);

\path[fill=fillColor] (232.31,319.77) rectangle (239.00,405.18);

\path[fill=fillColor] (239.74,319.77) rectangle (246.43,391.51);

\path[fill=fillColor] (247.17,319.77) rectangle (253.86,364.18);

\path[fill=fillColor] (254.60,319.77) rectangle (261.29,350.51);

\path[fill=fillColor] (262.03,319.77) rectangle (268.72,340.26);

\path[fill=fillColor] (269.46,319.77) rectangle (276.15,326.60);

\path[fill=fillColor] (276.89,319.77) rectangle (283.58,323.18);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.71,319.77) rectangle (283.58,555.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,316.74) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,385.06) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,453.39) {40};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,521.72) {60};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,319.77) --
	( 31.71,319.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,388.10) --
	( 31.71,388.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,456.42) --
	( 31.71,456.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,524.75) --
	( 31.71,524.75);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.63,317.02) --
	( 79.63,319.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (131.64,317.02) --
	(131.64,319.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (183.65,317.02) --
	(183.65,319.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (235.66,317.02) --
	(235.66,319.77);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 79.63,308.76) {Jan 13};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (131.64,308.76) {Jan 20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (183.65,308.76) {Jan 27};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (235.66,308.76) {Feb 03};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (157.65,296.72) {Symptom onset date};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,437.63) {Number of cases with a known infector/infectee pair};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 31.71,563.57) {A. Epidemic curve};
\end{scope}
\begin{scope}
\path[clip] (299.25,289.08) rectangle (567.99,578.16);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (299.25,289.08) rectangle (567.99,578.16);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (333.90,319.77) rectangle (562.49,555.50);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (499.08,484.95) {maximum observable};

\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (384.78,363.51) {minimum observable};

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (419.62,555.50) --
	(426.76,548.36) --
	(433.91,541.22) --
	(441.05,534.07) --
	(448.19,526.93) --
	(455.34,519.79) --
	(462.48,512.64) --
	(469.62,505.50) --
	(476.77,498.35) --
	(483.91,491.21) --
	(491.05,484.07) --
	(498.20,476.92) --
	(505.34,469.78) --
	(512.48,462.64) --
	(519.63,455.49) --
	(526.77,448.35) --
	(533.91,441.21) --
	(541.06,434.06) --
	(548.20,426.92) --
	(555.35,419.78) --
	(562.49,412.63);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (333.90,405.49) --
	(341.04,398.34) --
	(348.18,391.20) --
	(355.33,384.06) --
	(362.47,376.91) --
	(369.61,369.77) --
	(376.76,362.63) --
	(383.90,355.48) --
	(391.04,348.34) --
	(398.19,341.20) --
	(405.33,334.05) --
	(412.47,326.91) --
	(419.62,319.77);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (333.90,426.92) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (348.18,508.18) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (355.33,472.16) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.47,484.07) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.61,484.07) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (376.76,512.64) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (383.90,512.64) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (391.04,484.07) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (398.19,505.50) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (405.33,473.35) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (412.47,448.66) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (419.62,448.80) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (426.76,454.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (433.91,439.12) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (441.05,450.03) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (448.19,438.38) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (455.34,433.82) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (462.48,439.01) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (469.62,422.34) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (476.77,427.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (483.91,419.04) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (491.05,416.36) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (498.20,416.41) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (505.34,408.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (512.48,404.65) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (519.63,413.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (526.77,411.20) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (533.91,398.34) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (548.20,376.91) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (562.49,362.63) circle (  1.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,426.92) --
	(333.90,426.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,426.92) --
	(333.90,426.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,426.92) --
	(333.90,426.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (348.18,525.68) --
	(348.18,525.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (348.18,525.68) --
	(348.18,480.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (348.18,480.67) --
	(348.18,480.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.33,516.57) --
	(355.33,516.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.33,516.57) --
	(355.33,441.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.33,441.92) --
	(355.33,441.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.47,497.64) --
	(362.47,497.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.47,497.64) --
	(362.47,470.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.47,470.49) --
	(362.47,470.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,525.50) --
	(369.61,525.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,525.50) --
	(369.61,430.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,430.49) --
	(369.61,430.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (376.76,512.64) --
	(376.76,512.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (376.76,512.64) --
	(376.76,512.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (376.76,512.64) --
	(376.76,512.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (383.90,546.57) --
	(383.90,546.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (383.90,546.57) --
	(383.90,478.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (383.90,478.71) --
	(383.90,478.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (391.04,497.64) --
	(391.04,497.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (391.04,497.64) --
	(391.04,470.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (391.04,470.49) --
	(391.04,470.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (398.19,505.50) --
	(398.19,505.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (398.19,505.50) --
	(398.19,505.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (398.19,505.50) --
	(398.19,505.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (405.33,503.89) --
	(405.33,503.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] (405.33,503.89) --
	(405.33,448.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] (405.33,448.89) --
	(405.33,448.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] (412.47,519.07) --
	(412.47,519.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (412.47,519.07) --
	(412.47,399.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] (412.47,399.06) --
	(412.47,399.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] (419.62,501.93) --
	(419.62,501.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] (419.62,501.93) --
	(419.62,415.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (419.62,415.31) --
	(419.62,415.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (426.76,488.00) --
	(426.76,488.00);
